Manuscript figures

### 2021-10-08 docs/manuscript_figures.Rmd
Update docs for manuscript and tools to get final produ ct

## Results
### Learning rate comparison

```{r}
library(tidyverse)
# Define function
get_curves <- function(experiment_name,
                       step = 59,
                       path = here('results/scalar/compare_lr')){
    # Get file names
    fns <- list.files(path, 
                      pattern = experiment_name,
                      full.names = T)
    fns <- fns[str_detect(fns, 'Validate')]

# Clean scalar csvs
curves_lr_01 <- get_curves('unet_lr_01')
curves_lr_001 <- get_curves('unet_lr_001')
curves_lr_0001 <- get_curves('unet_lr_0001')
curves_lr_00001 <- get_curves('unet_lr_00001')
curves_lr_000001 <- get_curves('unet_lr_000001')

types <- c('AA', 'IoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
        } else{item <- type}
    list(curves_lr_01[[item]],
         curves_lr_001[[item]],
         curves_lr_0001[[item]],
         curves_lr_00001[[item]],
         curves_lr_000001[[item]]) %>% 
        reduce(left_join, by = "Step") %>% 
        `colnames<-`(c("Epoch", '0.1', '0.01', 
                       '0.001', '0.0001', '0.00001')) %>% 
        mutate(Item = type) %>% 
        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
                     names_to = 'Learning rate', 
                     values_to = 'Value')
})) %>% mutate(Item = factor(Item, levels = types))

# Get final plot
curves_lr <- ggplot(content, aes(x = Epoch, y = Value)) +
    # geom_line(aes(color = `Learning rate`)) +
    geom_smooth(aes(color = `Learning rate`), span = 0.2,
                se = F, size = 0.6) +
    scale_color_brewer(palette = "Set1") +
    facet_wrap(~Item, scales = 'free_y') +
    labs(y = 'Accuracy') +
    theme_bw() +
    theme(legend.position = 'top')
ggsave(here('docs/figures/curves_lr.png'),
       curves_lr,
       width = 8, height = 5, dpi = 300)
```

### Overall results
#### Metrics
```{r}
library(glue)
# Get file names
fns <- list.files(here(
    file.path('results/scalar',
              'unet_score08_hardiness20_epoch200')), 
    full.names = T)

@@

acc <- tb %>% filter(Metric %in% types) %>% 
    mutate(mean = round(mean * 100, 2),
           sd = round(sd * 100, 2),
           Class = factor(Metric, levels = types),
           Accuracy = glue(
               paste0('{format(round(mean, digits = 2), nsmall = 2)}',
                      '\u00B1{format(round(sd, digits = 2), nsmall = 2)} %'))) %>% 
    dplyr::select(Class, Accuracy) %>% 
    arrange(Class)
write.csv(acc, here('docs/figures/acc_last10epoch.csv'),
          row.names = F)
```

@@

```{r}
library(here)
# Get file names
fns <- list.files(here(
    file.path('results/scalar',
              'unet_score08_hardiness20_epoch200')), 
    full.names = T)

@@

ggsave(here('docs/figures/curves_final_mod.png'),
       curves,
       width = 8, height = 5, dpi = 300)
```

## Sensitivity analysis
### Quality weights
#### Score factor
```{r}
# Clean scalar csvs
curves_no_weight <- get_curves(
    'unet_no_weight',
    path = here('results/scalar/compare_score'))
curves_score02 <- get_curves(
    'unet_score_02',
    path = here('results/scalar/compare_score'))
curves_score08 <- get_curves(
    'unet_score_08',
    path = here('results/scalar/compare_score'))
curves_score16 <- get_curves(
    'unet_score_16',
    path = here('results/scalar/compare_score'))
curves_score32 <- get_curves(
    'unet_score_32',
    path = here('results/scalar/compare_score'))
curves_score100 <- get_curves(
    'unet_score_100',
    path = here('results/scalar/compare_score'))

types <- c('AA', 'IoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
        } else{item <- type}
    list(curves_no_weight[[item]],
         curves_score02[[item]],
         curves_score08[[item]],
         curves_score16[[item]],
         curves_score32[[item]],
         curves_score100[[item]]) %>% 
        reduce(left_join, by = "Step") %>% 
        `colnames<-`(c("Epoch", '0', '0.2', '0.8', 
                       '1.6', '3.2', '10')) %>% 
        mutate(Item = type) %>% 
        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
                     names_to = 'Weight factor', 
                     values_to = 'Value')
})) %>% mutate(Item = factor(Item, levels = types),
               `Weight factor` = factor(
                   `Weight factor`, 
                   levels = c('0', '0.2', '0.8', 
                              '1.6', '3.2', '10')))

# Get final plot
curves_score <- ggplot(content, aes(x = Epoch, y = Value)) +
    # geom_line(aes(color = `Weight factor`)) +
    geom_smooth(aes(color = `Weight factor`), span = 0.2,
                se = F, size = 0.6) +
    scale_color_manual(
        values = c('Black', 
                   RColorBrewer::brewer.pal(5, "Dark2"))) +
    # scale_color_brewer(palette = "Dark2") +
    facet_wrap(~Item, scales = 'free_y') +
    labs(y = 'Accuracy') +
    theme_bw() +
    theme(legend.position = 'top') +
    guides(color = guide_legend(nrow = 1))
ggsave(here('docs/figures/curves_score.png'),
       curves_score,
       width = 8, height = 5, dpi = 300)
```

#### Hardiness
```{r}
# Clean scalar csvs
curves_score08_nohard <- get_curves(
    'unet_score_08',
    path = here('results/scalar/compare_score'))
curves_hard2 <- get_curves(
    'unet_score08_hardiness_2',
    path = here('results/scalar/compare_score'))
curves_hard4 <- get_curves(
    'unet_score08_hardiness_4',
    path = here('results/scalar/compare_score'))
curves_hard6 <- get_curves(
    'unet_score08_hardiness_6',
    path = here('results/scalar/compare_score'))

types <- c('AA', 'IoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
        } else{item <- type}
    list(curves_score08_nohard[[item]],
         curves_hard2[[item]],
         curves_hard4[[item]],
         curves_hard6[[item]]) %>% 
        reduce(left_join, by = "Step") %>% 
        `colnames<-`(c("Epoch", '0', '2', '4', '6')) %>% 
        mutate(Item = type) %>% 
        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
                     names_to = 'Weight scale', 
                     values_to = 'Value')
})) %>% mutate(Item = factor(Item, levels = types),
               `Weight scale` = factor(
                   `Weight scale`, 
                   levels = c('0', '2', '4', '6')))

# Get final plot
curves_hard <- ggplot(content, aes(x = Epoch, y = Value)) +
    geom_smooth(aes(color = `Weight scale`), span = 0.2,
                se = F, size = 0.6) +
    scale_color_manual(
        values = c('Black', 
                   RColorBrewer::brewer.pal(3, "Dark2"))) +
    # scale_color_brewer(palette = "Dark2") +
    facet_wrap(~Item, scales = 'free_y') +
    labs(y = 'Accuracy') +
    theme_bw() +
    theme(legend.position = 'top') +
    guides(color = guide_legend(nrow = 1))
ggsave(here('docs/figures/curves_hard.png'),
       curves_hard,
       width = 8, height = 5, dpi = 300)
```

@@

```{r}

```

>>>>

## Results
### Random forest evaluation
#### Holdout validate

```{r}
load(here("data/north/final_res.rda"))
cf <- confusionMatrix(data = final_res$.predictions[[1]]$.pred_class, 
                      reference = final_res$.predictions[[1]]$landcover)
save(cf, file = here('docs/figures/rf_holdout_conf.rda'))

conf <- cf$table
# row is truth, column is predict
# match with python sklearn
conf <- matrix(as.numeric(conf), nrow = nrow(conf), ncol = ncol(conf))
conf <- t(conf)

# Calculate producer's accuracy
prac <- sapply(1:7, function(n){
  conf[n, n] / rowSums(conf)[n]
})

acc_test <- data.frame(class = 1:7,
                       producer_acc = prac)
write.csv(acc_test, here('docs/figures/rf_holdout_acc.csv'),
          row.names = F)
```

#### Independent test

```{r}
library(terra)
library(parallel)
library(ramify)
library(ranger)
library(parsnip)
library(tidymodels)
library(caret)

tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson'))
imgs <- rast(file.path(
        "/Volumes/elephant/pred_stack",
        paste0(tiles$tile[1], ".tif")))
sample_test <- read_sf(here('data/north/plys_holdout_check.geojson')) %>% 
  st_join(tiles) %>% st_transform(crs = crs(imgs)) %>% 
  vect(); rm(imgs)

test_rf_features <- do.call(
  rbind,
  mclapply(unique(sample_test$tile),
    function(tile_nm) {
      # Get imgs
      imgs <- rast(file.path(
        "/Volumes/elephant/pred_stack",
        paste0(tile_nm, ".tif")
      ))

      # get samples
      samples_this <- sample_test[sample_test$tile == tile_nm, ]
      trainings_this <- do.call(
          rbind, 
          lapply(1:nrow(samples_this), function(n){
          sample_n <- samples_this[n, ]
          terra::extract(
              imgs, sample_n) %>%
              mutate(landcover = sample_n$landcover) %>%
              dplyr::select(-ID)
      }))
      rm(imgs, samples_this)
      gc()
      trainings_this
    }, mc.cores = 4)
)
save(test_rf_features, 
     file = file.path(here("data/north"), 
                      "test_rf_features.rda"))

load(here("data/north/guess_rf_md.rda"))
test_rf_features <- test_rf_features %>% na.omit()
pred <- predict(guess_rf_md$fit, 
                test_rf_features %>% select(-landcover))
pred <- argmax(pred$predictions)
pred <- data.frame(predict = pred,
                   test = test_rf_features$landcover)
lc_types <- data.frame(id = 1:7,
                       type = c('cropland', 'forest', 'grassland',
                                'shrubland', 'water', 'built-up',
                                'bareland'))
pred_eval <- left_join(pred, lc_types, 
                       by = c('test' = 'type')) %>% 
    dplyr::select(-test) %>% 
    rename(test = id) %>% 
    mutate(predict = as.factor(predict),
           test = as.factor(test))

cf <- confusionMatrix(data = pred_eval$predict, 
                      reference = pred_eval$test)
save(cf, file = here('docs/figures/rf_test_conf.rda'))

acc_test <- cf$byClass
write.csv(acc_test, here('docs/figures/rf_test_acc.csv'),
          row.names = F)
```

#### Human checking
```{r}
library(sf)
library(glue)
library(here)

tile_nm <- 'catalog_sample_tiles_update.geojson'
tiles <- here(glue('results/north/{tile_nm}')) %>% 
  read_sf(); rm(tile_nm)
tiles <- tiles %>% 
  mutate(quality = glue("({score}, {hardiness})")) %>% 
  st_drop_geometry() %>% 
  mutate(quality = factor(quality))

ggplot(tiles, aes(quality)) +
  geom_bar(color = 'black',fill = 'cyan3') +
  xlab('Quality (correctness, difficulty)') +
  ylab('Count') +
  theme_bw()

quality_fig <- ggplot(
  tiles,
  aes(fill = factor(hardiness), x = score)) + 
  geom_bar(position = "stack") +
  scale_fill_brewer('Difficulty', palette = "Dark2") +
  xlab('Correctness') +
  ylab('Count') +
  theme_bw()

ggplot(
  tiles,
  aes(fill = factor(hardiness), x = score)) + 
  geom_bar(position = "stack") +
  coord_polar("x") +
  theme_bw()

ggsave(here('docs/figures/humancheck_quality.png'),
       quality_fig,
       width = 4, height = 4, dpi = 300)
```

### Overall results
#### Metrics
```{r}
library(glue)
library(stringr)
library(caret)

# Validate
# Get file names
fns <- list.files(here(
    'results/scalar/full_runs'), 
    pattern = 'unet_k15_only_nopad_clr_200epc',
    full.names = T)

@@

acc <- tb %>% filter(Metric %in% types) %>% 
    mutate(mean = round(mean * 100, 2),
           sd = round(sd * 100, 2),
           Class = factor(Metric, levels = types),
           Accuracy = glue(
               paste0('{format(round(mean, digits = 2), nsmall = 2)}',
                      '\u00B1{format(round(sd, digits = 2), nsmall = 2)} %'))) %>% 
    dplyr::select(Class, Accuracy) %>% 
    arrange(Class)
write.csv(acc, here('docs/figures/k15_only_acc_last10epoch.csv'),
          row.names = F)

# Test
sample_test <- read_sf(here('data/north/plys_holdout_check.geojson'))
pred <- rast(here(file.path('results/dl/prediction',
                            'unet_k15_only_clr_200epc',
                            'landcover_north.tif')))
sample_test <- vect(sample_test %>% st_transform(crs = crs(pred)))
pred_eval <- terra::extract(pred, sample_test, list = T)
pred_eval <- do.call(rbind, lapply(1:length(pred_eval), function(n){
    rst_vals <- pred_eval[[n]][[1]]
    data.frame(predict = rst_vals,
               test = sample_test[n, ]$landcover)
}))

lc_types <- data.frame(id = 1:7,
                       type = c('cropland', 'forest', 'grassland',
                                'shrubland', 'water', 'built-up',
                                'bareland'))
pred_eval <- left_join(pred_eval, lc_types, by = c('test' = 'type')) %>% 
    dplyr::select(-test) %>% 
    rename(test = id) %>% 
    mutate(predict = as.factor(predict),
           test = as.factor(test))
cf <- confusionMatrix(data=pred_eval$predict, reference = pred_eval$test)
save(cf, file = here('docs/figures/test_conf.rda'))

acc_test <- cf$byClass
write.csv(acc_test, here('docs/figures/test_acc.csv'),
          row.names = F)
```

@@

```{r}
library(here)
library(ggplot2)
library(ggpubr)

# Get file names
fns <- list.files(here(
    'results/scalar/full_runs'), 
    pattern = 'unet_k15_only_nopad_clr_200epc', 
    full.names = T)

@@

ggsave(here('docs/figures/curves_k15_only_final_mod.png'),
       curves,
       width = 8, height = 5, dpi = 300)
```

#### Prediction examples

Provide some prediction examples of different LC types. Then provide an overall map. Could put them together.

```{r, eval=FALSE}
library(glue)

pred_path <- here(file.path('results/dl/prediction',
                            'unet_k15_only_clr_200epc',
                            'landcover_north_withwl.tif'))
score_path <- here(file.path('results/dl/prediction',
                             'unet_k15_only_clr_200epc',
                             'landcover_confidence_north_withwl.tif'))
# Partial GRASS command to get standard deviation
execGRASS('r.in.gdal', flags = c("o", "overwrite"),
          input = score_path,
          band = 1,
          output = "score")
execGRASS('r.in.gdal', flags = c("o", "overwrite"),
          input = pred_path,
          band = 1,
          output = "pred")
execGRASS("g.region", raster = "score")
execGRASS('r.stats.zonal', flags = c('overwrite'),
          base = 'pred',
          cover = 'score',
          method = 'stddev',
          output = 'class_stddev')
dst_path <- here(file.path('results/dl/prediction',
                             'unet_k15_only_clr_200epc',
                             'class_stddev.tif'))
execGRASS('r.out.gdal', flags = c("overwrite"),
          parameters = list(input = 'class_stddev', 
                            output = dst_path,
                            createopt = "COMPRESS=LZW"))

pred_path <- here(file.path('results/dl/prediction',
                            'unet_k15_only_clr_200epc',
                            'landcover_north_withwl.tif'))
score_path <- here(file.path('results/dl/prediction',
                             'unet_k15_only_clr_200epc',
                             'landcover_confidence_north_withwl.tif'))
pred <- rast(pred_path)
score <- rast(score_path)
std <- rast(dst_path)
means <- zonal(score, pred, "mean", na.rm = TRUE)
stds <- zonal(std, pred, "mean", na.rm = TRUE)

mean_std <- data.frame(means) %>% 
  left_join(data.frame(stds)) %>% 
  `colnames<-`(c('landcover', 'mean', 'std')) %>% 
  mutate(Confidence = glue(
               paste0('{format(round(mean, digits = 2), nsmall = 2)}',
                      '\u00B1{format(round(std, digits = 2), nsmall = 2)}'))) %>% 
  left_join(color_tb %>% select(id, type), by = c('landcover' = 'id')) %>% 
  rename(Landcover = type) %>% select(Landcover, Confidence)
save(mean_std, file = here('docs/figures/conf_mean_std.rda'))
```

```{r}
library(terra)
library(stars)
library(tmap)
library(ggpubr)
library(gridExtra)

load(here('docs/figures/conf_mean_std.rda'))
pred_path <- here(file.path('results/dl/prediction',
                           'unet_k15_only_clr_200epc',
                           'landcover_north_withwl.tif'))
color_tb <- data.frame(
    id = 1:8,
    type = c("Cropland", "Forest", 
             "Grassland", "Shrubland", 
             "Water", 'Built-up', "Bareland", 
             'Wetland'),
    color = c('#ff7f00', '#074702', '#b2df8a',
              '#33a02c', '#3347f9', '#5a6057',
              '#fdbf6f', '#0ea591'))
# pred <- read_stars(pred_path)
pred <- rast(pred_path)
setCats(pred, value = color_tb$type, index = color_tb$id)
pred <- st_as_stars(pred)

# plot
# Get examples
tiles <- read_sf('data/geoms/tiles_nicfi_north.geojson')
id_selected <- c('1226-1012', '1227-1005', '1209-997', '1219-1017',
                 '1234-992', '1211-1008', '1236-1007','1220-995')
tiles <- tiles %>% filter(tile %in% id_selected) %>% 
    st_transform(crs = crs(rast(pred_path))) %>% 
    mutate(id = 1:nrow(.))
rst_tiles <- lapply(1:nrow(tiles), function(n){
    tm <- st_crop(pred, tiles %>% slice(n)) %>% 
        tm_shape() + 
        tm_raster("landcover_north", 
              n = 8, style = 'cat',
              labels = color_tb$type,
              palette = color_tb$color) +
        tm_layout(frame = F,
                  legend.show = F,
                  title.position = c(0, 0.9),
                  title = tiles %>% slice(n) %>% pull(id))
     tmap_grob(tm)
})
plot_left <- ggarrange(
    rst_tiles[[1]], rst_tiles[[2]], rst_tiles[[3]], 
    rst_tiles[[4]], ncol = 1, nrow = 4)
plot_right <- ggarrange(
    rst_tiles[[5]], rst_tiles[[6]], rst_tiles[[7]],
    rst_tiles[[8]], ncol = 1, nrow = 4)

tmap_mode("plot")
pred_final <- tm_shape(pred) +
    tm_raster("landcover_north", 
              title = "Land cover types",
              n = 8, style = 'cat',
              labels = color_tb$type,
              palette = color_tb$color) +
    tm_shape(tiles) +
    tm_borders("black", lwd = 1.2) +
    tm_text("id", col = 'black', fontface = "bold", size = 0.8) +
    tm_layout(frame = F,
              legend.show = F,
              outer.margins = c(0.02, 0.01, 0, 0.01),
              inner.margins = 0)
pred_final <- tmap_grob(pred_final)

# Get legend
r_df <- data.frame(x = 1:8, 
                   y = 1:8,
                   rst = as.factor(1:8))
legend_lc <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = rst)) +
    scale_fill_manual('Land cover',
                      values = color_tb$color, 
                      breaks = 1:8,
                      labels = color_tb$type) +
    theme_minimal() +
    theme(legend.position = 'right',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))+
    guides(fill = guide_legend(ncol = 2))
legend_lc <- get_legend(legend_lc)

tbl_theme <- gridExtra::ttheme_default(
    core = list(fg_params=list(cex = 0.6),
                bg_params = list(fill = 'gray95')),
    colhead = list(fg_params=list(cex = 0.7)),
    rowhead = list(fg_params=list(cex = 0.7)))
tbl_conf <- tableGrob(mean_std, rows = NULL, theme = tbl_theme)
legend_lc <- ggarrange(NA, tbl_conf, NA, legend_lc, NA,
                       ncol = 5, widths = c(1, 2, 1, 2, 1))

pred_final_plt <- ggarrange(pred_final, legend_lc, NA,
                        nrow = 3, heights = c(5, 1, 0.6))
pred_example <- ggarrange(plot_left, pred_final_plt, plot_right,
          ncol = 3, widths = c(1, 3, 1))
ggsave(here('docs/figures/pred_example.png'),
       pred_example,
       width = 7, height = 6, dpi = 300)
```

## Sensitivity analysis
### Quality weights
#### Correctness
```{r}
library(tidyverse)
library(gridExtra)

# Define function
get_curves <- function(experiment_name,
                       step = 59,
                       path = here('results/scalar/compare_score')){
    # Get file names
    fns <- list.files(path, 
                      pattern = experiment_name,
                      full.names = T)
    fns <- fns[str_detect(fns, 'Validate')]

# Clean scalar csvs
curves_no_weight <- get_curves(
    'unet_no_weight',
    path = here('results/scalar/compare_score'))
curves_k05 <- get_curves(
    'unet_k05_only',
    path = here('results/scalar/compare_score'))
curves_k15 <- get_curves(
    'unet_k15_only',
    path = here('results/scalar/compare_score'))
curves_k30 <- get_curves(
    'unet_k3_only',
    path = here('results/scalar/compare_score'))

types <- c('AA', 'mIoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
    } else if (type == 'mIoU'){
        item <- 'IoU'
    } else {item <- type}
    list(curves_no_weight[[item]],
         curves_k05[[item]],
         curves_k15[[item]],
         curves_k30[[item]]) %>% 
        reduce(left_join, by = "Step") %>% 
        `colnames<-`(c("Epoch", '0', '0.5', '1.5', '3.0')) %>% 
        mutate(Item = type) %>% 
        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
                     names_to = 'k of logistic function', 
                     values_to = 'Value')
})) %>% mutate(Item = factor(Item, levels = types),
               `k of logistic function` = factor(
                   `k of logistic function`, 
                   levels = c('0', '0.5', '1.5', '3.0')))

# Calculate mean and sd of last 10 epochs
content_plot <- content %>% 
  filter(Epoch >= 21) %>% 
  filter(Item %in% c('AA', 'mIoU')) %>% 
  group_by(Item, `k of logistic function`) %>% 
  summarise(Mean = mean(Value), 
            sd = sd(Value))

# Get final plot
curves_corr <- ggplot(
  content_plot, 
  aes(x = `k of logistic function`, y = Mean)) + 
  geom_point() +
  geom_errorbar(aes(ymin = Mean - sd, ymax = Mean + sd), width=.2,
                position = position_dodge(0.05)) +
  facet_wrap(~Item, scales = 'free_y') +
  labs(y = 'Value', x = expression(paste(k, ' of logistic function'))) +
  theme_bw()
# ggsave(here('docs/figures/sa_correctness.png'),
#        curves_corr,
#        width = 6.5, height = 2, dpi = 300)
```

#### Hardiness
```{r}
# Clean scalar csvs
curves_k15_nohard <- get_curves(
    'unet_k15_only',
    path = here('results/scalar/compare_score'))
curves_k15_h11 <- get_curves(
    'unet_k15_hard11',
    path = here('results/scalar/compare_score'))
curves_k15_h12 <- get_curves(
    'unet_k15_hard12',
    path = here('results/scalar/compare_score'))
curves_k15_h14 <- get_curves(
    'unet_k15_hard14',
    path = here('results/scalar/compare_score'))

types <- c('AA', 'mIoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
    } else if (type == 'mIoU'){
        item <- 'IoU'
    } else {item <- type}
    list(curves_k15_nohard[[item]],
         curves_k15_h11[[item]],
         curves_k15_h12[[item]],
         curves_k15_h14[[item]]) %>% 
        reduce(left_join, by = "Step") %>% 
        `colnames<-`(c("Epoch", '1', '1.1', '1.2', '1.4')) %>% 
        mutate(Item = type) %>% 
        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
                     names_to = 'Weight scale', 
                     values_to = 'Value')
})) %>% mutate(Item = factor(Item, levels = types),
               `Weight scale` = factor(
                   `Weight scale`, 
                   levels = c('1', '1.1', '1.2', '1.4')))

# Calculate mean and sd of last 10 epochs
content_plot <- content %>% 
  filter(Epoch >= 21) %>% 
  filter(Item %in% c('AA', 'mIoU')) %>% 
  group_by(Item, `Weight scale`) %>% 
  summarise(Mean = mean(Value), 
            sd = sd(Value))

# Get final plot
curves_diff <- ggplot(
  content_plot, 
  aes(x = `Weight scale`, y = Mean)) + 
  geom_point() +
  geom_errorbar(aes(ymin = Mean - sd, ymax = Mean + sd), width=.2,
                position = position_dodge(0.05)) +
  facet_wrap(~Item, scales = 'free_y') +
  labs(y = 'Value', x = expression(s[max])) +
  theme_bw()
# ggsave(here('docs/figures/sa_difficulty.png'),
#        curves_diff,
#        width = 6.5, height = 2, dpi = 300)

params_cost <- ggarrange(curves_corr, curves_diff,
                        nrow = 2)
ggsave(here('docs/figures/sa_loss_params.png'),
       params_cost,
       width = 6.5, height = 4, dpi = 300)
```

@@

```{r}
# Clean scalar csvs
curves_full <- get_curves(
    'unet_k15_only',
    path = here('results/scalar/compare_score'))
curves_one_tile <- get_curves(
    step = 19, 
    'unet_one_tile',
    path = here('results/scalar/compare_sampling'))
curves_random_34 <- get_curves(
    step = 19,
    'unet_random_34',
    path = here('results/scalar/compare_sampling'))
curves_hori_strip_34 <- get_curves(
    step = 19,
    'unet_hori_strip_34',
    path = here('results/scalar/compare_sampling'))
curves_vert_strip_34 <- get_curves(
    step = 18,
    'vert_strip_34',
    path = here('results/scalar/compare_sampling'))
curves_two_tile <- get_curves(
    step = 39, 
    'unet_two_tile',
    path = here('results/scalar/compare_sampling'))
curves_random_67 <- get_curves(
    step = 39,
    'unet_random_67',
    path = here('results/scalar/compare_sampling'))
curves_hori_strip_67 <- get_curves(
    step = 39,
    'unet_hori_strip_67',
    path = here('results/scalar/compare_sampling'))
curves_vert_strip_67 <- get_curves(
    step = 39,
    'vert_strip_67',
    path = here('results/scalar/compare_sampling'))

types <- c('AA', 'mIoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
    } else if (type == 'mIoU'){
        item <- 'IoU'
    } else {item <- type}
    list(curves_full[[item]],
         curves_one_tile[[item]],
         curves_random_34[[item]],
         curves_hori_strip_34[[item]],
         curves_vert_strip_34[[item]],
         curves_two_tile[[item]],
         curves_random_67[[item]],
         curves_hori_strip_67[[item]],
         curves_vert_strip_67[[item]]) %>% 
        reduce(left_join, by = "Step") %>% 
        `colnames<-`(c("Epoch", '3 samples/tile', '1 sample/tile', '34% (randomly)', 
                       '34% (Hori-strip)', '34% (Vert-strip)',
                       '2 samples/tile', '67% (randomly)', 
                       '67% (Hori-strip)', '67% (Vert-strip)')) %>% 
        mutate(Item = type) %>% 
        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
                     names_to = 'Sampling method', 
                     values_to = 'Value')
})) %>% mutate(Item = factor(Item, levels = types),
               `Sampling method` = factor(
                   `Sampling method`, 
                   levels = c('3 samples/tile', '1 sample/tile', '34% (randomly)', 
                       '34% (Hori-strip)', '34% (Vert-strip)',
                       '2 samples/tile', '67% (randomly)', 
                       '67% (Hori-strip)', '67% (Vert-strip)')))

# Calculate mean and sd of last 10 epochs
content_plot <- content %>% 
  filter(Epoch >= 21) %>% 
  filter(`Sampling method` %in% 
           c('1 sample/tile', '34% (randomly)',
             '2 samples/tile', '67% (randomly)',
             '3 samples/tile')) %>% 
  filter(Item %in% c('AA', 'mIoU')) %>% 
  rename(`Sampling strategy` = `Sampling method`) %>% 
  group_by(Item, `Sampling strategy`) %>% 
  summarise(Mean = mean(Value), 
            sd = sd(Value))

# Get final plot
curves_sampling <- ggplot(
  content_plot, aes(x = `Sampling strategy`, y = Mean)) + 
  geom_point() +
  geom_errorbar(aes(ymin = Mean - sd, ymax = Mean + sd), 
                width =.2,
                position = position_dodge(0.05)) +
  facet_wrap(~Item, scales = 'free_y') +
  labs(y = 'Value') +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  NULL + theme_bw()
ggsave(here('docs/figures/sa_sampling.png'),
       curves_sampling,
       width = 6.5, height = 2.5, dpi = 300)
```

## Appendix
### Evaluation of LC products

Use our independent test dataset to evaluate the quality of LC products used in this study.

```{r}
library(here)
library(sf)
library(terra)
library(caret)

sample_test <- vect(here('data/north/plys_holdout_check.geojson'))
lc_types <- data.frame(id = 1:10,
                       type = c('cropland', 'forest', 'grassland',
                                'shrubland', 'wetland', 'water', 
                                "tundra", 'built-up',
                                'bareland', 'snow/ice'))
tiles <- read_sf(
    here('data/geoms/tiles_nicfi_north.geojson'),
    stringsAsFactors = F) %>% vect()

# ESA LC
esaglc <- rast(here('data/landcovers/esaglc_rcl.tif'))
esaglc_eval <- terra::extract(esaglc, sample_test, list = T, touches = T)
esaglc_eval <- do.call(rbind, lapply(1:length(esaglc_eval), function(n){
    rst_vals <- esaglc_eval[[n]][[1]]
    data.frame(product = rst_vals,
               test = sample_test[n, ]$landcover)
}))

esaglc_eval <- left_join(esaglc_eval, lc_types, 
                       by = c('test' = 'type')) %>% 
    dplyr::select(-test) %>% 
    rename(test = id) %>% 
    filter(product != 5) %>% 
    mutate(product = as.factor(product),
           test = as.factor(test))
cf <- confusionMatrix(data=esaglc_eval$product, reference = esaglc_eval$test)
save(cf, file = here('docs/figures/esaglc_test_conf.rda'))

acc_test <- cf$byClass
write.csv(acc_test, here('docs/figures/esaglc_test_acc.csv'),
          row.names = F)

# fromglc
fromglc <- rast(here('data/landcovers/fromglc_rcl.tif'))
fromglc_eval <- terra::extract(fromglc, sample_test, list = T, touches = T)
fromglc_eval <- do.call(rbind, lapply(1:length(fromglc_eval), function(n){
    rst_vals <- fromglc_eval[[n]][[1]]
    data.frame(product = rst_vals,
               test = sample_test[n, ]$landcover)
}))

fromglc_eval <- left_join(fromglc_eval, lc_types, 
                       by = c('test' = 'type')) %>% 
    dplyr::select(-test) %>% 
    rename(test = id) %>% 
    filter(product != 5) %>% 
    mutate(product = as.factor(product),
           test = as.factor(test))
cf <- confusionMatrix(data=fromglc_eval$product, reference = fromglc_eval$test)
save(cf, file = here('docs/figures/fromglc_test_conf.rda'))

acc_test <- cf$byClass
write.csv(acc_test, here('docs/figures/fromglc_test_acc.csv'),
          row.names = F)

# gfsad
gfsad <- rast(here('data/landcovers/gfsad_rcl.tif'))
gfsad_eval <- terra::extract(gfsad, sample_test, list = T, touches = T)
gfsad_eval <- do.call(rbind, lapply(1:length(gfsad_eval), function(n){
    rst_vals <- gfsad_eval[[n]][[1]]
    data.frame(product = rst_vals,
               test = sample_test[n, ]$landcover)
}))

gfsad_eval <- left_join(gfsad_eval, lc_types, 
                       by = c('test' = 'type')) %>% 
    dplyr::select(-test) %>% 
    rename(test = id) %>% 
    mutate(test = ifelse(test == 6, 6, ifelse(test == 1, 1, 0))) %>% 
    mutate(product = as.factor(product),
           test = as.factor(test))
cf <- confusionMatrix(data = gfsad_eval$product, reference = gfsad_eval$test)
save(cf, file = here('docs/figures/gfsad_test_conf.rda'))

acc_test <- cf$byClass
write.csv(acc_test, here('docs/figures/gfsad_test_acc.csv'),
          row.names = F)

# Tansis
tansis <- rast(list.files(here('data/tansis'), 
                          full.names = T, pattern = '.tif$'))
tansis <- tansis$TZ__7
tansis <- project(tansis, crs(sample_test), method = 'near')
tansis[is.na(tansis)] <- 0

tansis_eval <- terra::extract(tansis, sample_test, list = T, touches = T)
tansis_eval <- do.call(rbind, lapply(1:length(tansis_eval), function(n){
    rst_vals <- tansis_eval[[n]][[1]]
    data.frame(product = rst_vals,
               test = sample_test[n, ]$landcover)
}))

tansis_eval <- left_join(tansis_eval, lc_types, 
                         by = c('test' = 'type')) %>% 
  dplyr::select(-test) %>% 
  rename(test = id) %>% 
  mutate(test = ifelse(test == 1, 1, 0)) %>% 
  na.omit() %>% 
  mutate(product = as.factor(product),
         test = as.factor(test))
cf <- confusionMatrix(data = tansis_eval$product, 
                      reference = tansis_eval$test,
                      positive = "1")
save(cf, file = here('docs/figures/tansis_test_conf.rda'))

acc_test <- cf$byClass
write.csv(acc_test, here('docs/figures/tansis_test_acc.csv'))
```

### RF tuning

```{r}
library(here)
library(dplyr)
library(ramify)
library(ranger)
library(parsnip)
library(tidymodels)
library(vip)
library(dials)
library(ggplot2)
library(ggpubr)

load("~/Dropbox/research/hrlcm/data/north/forest_vip.rda")
vip_figure <- vip(forest_vip, 
    num_features = forest_vip$fit$num.independent.variables,
    aesthetics = list(color = "transparent", 
                      fill = "red")) +
    theme_light()
